Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)

### 2023-11-13 manuscript_BiSC.tex

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{authblk} % this is for multiple authors 
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{cleveref}

@@

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Model} & \textbf{Pollutant} & \textbf{Dataset campaign} & \textbf{N} & \textbf{R\textsuperscript{2} (10-CV)} & \textbf{RMSE (10-CV)} \\ \hline
HM & NO\textsubscript{2} & BiSC-home & 1232 & 0.64 & 7.5 \\ \hline
HM & PM\textsubscript{2.5} & BiSCAPE & 161 & 0.66 & 3.45 \\ \hline
HM & BC & BiSCAPE & 74 & 0.86 & ... \\ \hline
HM & Fe & BiSCAPE & ... & ... & ... \\ \hline
HM & Cu & BiSCAPE & ... & ... & ... \\ \hline
HM & Zn & BiSCAPE & ... & ... & ... \\ \hline
LUR & NO\textsubscript{2} & BiSC-home & ... & ... & ... \\ \hline
LUR & PM\textsubscript{2.5} & BiSCAPE & ... & ... & ... \\ \hline
LUR & BC & BiSCAPE & ... & ... & ... \\ \hline
LUR & Fe & BiSCAPE & ... & ... & ... \\ \hline
LUR & Cu & BiSCAPE & ... & ... & ... \\ \hline
LUR & Zn & BiSCAPE & ... & ... & ... \\ \hline
\end{tabular}
\caption{Your caption here}
\label{table:your_label_here}
\end{table}

>>>>

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{authblk} % this is for multiple authors 
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllll}
\toprule
\textbf{Model} & \textbf{Pollutant} & \textbf{Dataset campaign} & \textbf{N} & \textbf{R2 (10-CV)} & \textbf{RMSE (10-CV)} \\
\midrule
\multirow{6}{*}{LUR} & NO2 & BiSC-home & ... & ... & ... \\
& PM2.5 & BiSCAPE & ... & ... & ... \\
& BC & BiSCAPE & ... & ... & ... \\
& Fe & BiSCAPE & ... & ... & ... \\
& Cu & BiSCAPE & ... & ... & ... \\
& Zn & BiSCAPE & ... & ... & ... \\
\midrule
\multirow{6}{*}{HM} & NO2 & BiSC-home & 1232 & 0.64 & 7.5 \\
& PM2.5 & BiSCAPE & ... & ... & ... \\
& BC & BiSCAPE & ... & ... & ... \\
& Fe & BiSCAPE & ... & ... & ... \\
& Cu & BiSCAPE & ... & ... & ... \\
& Zn & BiSCAPE & ... & ... & ... \\
\bottomrule
\end{tabular}
\caption{Descriptive caption for the table.}
\label{tab:my_label}
\end{table}
